---
title: "Homework #5"
output: github_document
author: David Nemirovsky
date: 11/18/20
---

```{r setup, include = F}
library(tidyverse)
library(rvest)
library(patchwork)

knitr::opts_chunk$set(
  fig.width = 7,
  fig.asp = .6,
  out.width = "95%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Read in the data:

```{r read and tidy homicide data, message = F}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved")
    ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

Let's look at this a bit:

```{r summarize totals, message = F}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r prop test, results = 'hide'}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate:

```{r iteration}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

Plot:

```{r plot}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

First, let's make a dataframe with a path for each file:

```{r path df}
path_df = 
  tibble(path = list.files("lda_data")) %>% 
  mutate(path = str_c("lda_data/", path))
```

Now, let's iterate the `read_csv` function across the dataframe using `map`:

```{r read data iteration, message = F}
lda_df = 
  path_df %>% 
  mutate(data = map(.x = path, ~read_csv(.x)))
```

Next, let's tidy this dataframe:

```{r tidy df, warning = F}
lda_df = 
  lda_df %>% 
  unnest() %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "observation"
  ) %>% 
  mutate(week = str_remove(week, "week_"),
         week = as.numeric(week), 
         arm_sub = str_remove(path, "^lda_data/"),
         arm_sub = str_remove(arm_sub, ".csv$")) %>% 
  separate(arm_sub, c("arm", "subject")) %>% 
  relocate(arm, subject) %>% 
  select(-path)
```

Finally, some spaghetti plots:

```{r spaghetti plots}
con_plot = 
  lda_df %>% 
  filter(arm == "con") %>% 
  ggplot(aes(x = week, y = observation, color = subject)) +
  geom_line() +
  labs(
    title = "Subjects in Control Arm",
    x = "Week",
    y = "Observation"
  ) +
  scale_colour_discrete(name = "Subject:") +
  theme(plot.title = element_text(hjust = 0.5))

exp_plot = 
  lda_df %>% 
  filter(arm == "exp") %>% 
  ggplot(aes(x = week, y = observation, color = subject)) +
  geom_line() +
  labs(
    title = "Subjects in Experimental Arm",
    x = "Week",
    y = "Observation"
  ) +
  scale_colour_discrete(name = "Subject:") +
  theme(plot.title = element_text(hjust = 0.5))

con_plot + exp_plot
```

According to the two plots above, the subjects in the control arm showed random, varied changes over time throughout the longitudinal study. The subjects in the experimental arm, however, showed a generally gradual increase over the course of the 8-week longitudinal study.




